\section{Group Members Contribution}

% For each group member, describe in detail the contribution to the project.

\begin{description}
\item \textbf{Alberto Crivellari:} implemented rest of scooter, scooterrack and model, implemented servlets for scooter, scooterrack and rental for the manage page section, wrote the section regarding class diagrams, data dictionary:entity table and main functionalities, and helped with the rest API section.

\item \textbf{Nick Kuijpers:}
Worked on the Dashboard with Sara. Did the Scooterrack, paymentwithoutsubscriptions servlets and the customer rest API. Made mockups about the scooterrack page and model page. Made the sequence diagram of the customer rest API. Wrote in the report the objectives chapter and the presentation logic layer.

\item \textbf{Shiva Gharehzad:}
Worked on the database design, ER schema, SQL for database , inserting data, data layer description, rest API of the model and scooters, searching model by name in rest part,  servlet for scooter, class diagram, wrote parts of the report. 

\item \textbf{Borwoei Huang:}
Did the login page for authorized administrators to log in to our web application. Filter is built to block the unauthorized users. To manage the administrator account, creation ad searching of the administrator functions were made. Administrator creation servlet manages multipart. Worked on the administrator rest api with AJAX administrator searching form reading the output of Id or Email admin-searching. Wrote parts of the report.


\item \textbf{Sreeshalini Mada:}
Made administrator rest api for searching the admin table in the database. Wrote parts of the report.

\item \textbf{Sara Niknamhesar:}
Working on the dashboard section with Nick, doing the topLocation, scooterRackList, and Revenue sections of the servlet, designing general Mockups about the display process on the dashboard and other panel pages, designing class diagrams and writing them in the Business Logic Layer section.

\item \textbf{Paria Tahan:}
Completed the design of the database also created the ER-Schema. Built SQL for database schema and data insertion. Worked on the Model (Create, Update, List), Customer (List), Subscription (Create, Update, List) and Payment method (Update, List) from manage pages. Created the servlet file for each of the resources except Admin. Generated the manage pages class diagram. Helped with the Balsamiq mockups and writing the report.



\end{description}
