\section{Objectives}
%Brief description of the overall objectives of your system.
%What your system will be used for? Why is it important? What problems does it solve?
The objective of this project is to develop a web application that assists managers in the scooter business with their daily operations. The scope of the project was defined for the Master in computer engineering program and involved 10 students at the beginning, with 7 students ultimately completing the project. 

\vspace{10pt}

The web applicationwill managers  analyze application allows, product, and staff data to make informed business decisions. The application will enable basic modifications such as adding or deleting data, and it is critical that the owner can perform these changes when necessary. The system will provide a comprehensive overview of all necessary information, allowing for long-term decision-making based on data analysis.

\vspace{10pt}

The main goal of the project is to create a platform that streamlines business processes, ultimately increasing efficiency and profitability. This application will be designed with user-friendly interfaces and interactive features, making it accessible to a wide range of users. The project will leverage modern web technologies to ensure the application is scalable and flexible enough to accommodate future business growth.

\vspace{10pt}

In summary, this project aims to create a web application that provides managers with the necessary tools to analyze and manage their business, ultimately improving their overall performance.





